Supporting Information:\\Conformational plasticity of phospholipid headgroups in simulations and experiments

### 2021-05-02 manuscriptPGPEsuppl.tex
PG OP plot.

\author{\scriptsize Am{\'e}lie Bacle}
\affiliation{Laboratoire Coop\'{e}ratif "Lipotoxicity and Channelopathies - ConicMeds", Universit\'{e} de Poitiers, 1 rue Georges Bonnet, 86000 Poitiers, France }

\author{\scriptsize Pavel Buslaev}
\affiliation{\tiny Nanoscience Center and Department of Chemistry, University of Jyväskylä, P.O. Box 35, 40014 Jyväskylä, Finland}
\affiliation{Research Center for Molecular Mechanisms of Aging and Age-related Diseases, Moscow Institute of Physics and Technology, 141701 Dolgoprudny, Russia}

>>>>

\author{\small Am{\'e}lie Bacle}
\affiliation{\tiny Laboratoire Coop\'{e}ratif "Lipotoxicity and Channelopathies - ConicMeds", Universit\'{e} de Poitiers, 1 rue Georges Bonnet, 86000 Poitiers, France }

\author{Pavel Buslaev}
\affiliation{Nanoscience Center and Department of Chemistry, University of Jyväskylä, P.O. Box 35, 40014 Jyväskylä, Finland}
\affiliation{Research Center for Molecular Mechanisms of Aging and Age-related Diseases, Moscow Institute of Physics and Technology, 141701 Dolgoprudny, Russia}
